---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
require( lubridate )

knitr::opts_chunk$set( echo = TRUE )

if ( !exists( "multiCities_gl7" ) ||
     !exists( "BRStats" ) ||
     today() - max( BRStats$date ) > days( 1 ) )
{
  source( "savePlots.R" )
}
```
# Gráficos sobre a pandemia de COVID-19 no Brasil
Atualizados diariamente, se tudo correr bem :smile:

## 1 - Estados Selecionados, Índice de Crescimento de Óbitos
```{r multistates_plot, echo=FALSE, message=FALSE, warning=FALSE}
multiStates_gl7
```

## 2 - Capitais Selecionadas, Índice de Crescimento de Óbitos
```{r multicities_plot, echo=FALSE, message=FALSE, warning=FALSE}
multiCities_gl7
```

## 3 - Nacional
```{r brasil_plots, echo=FALSE, message=FALSE, warning=FALSE}
sumStates_gl7
sumStates_m7
```

## 4 - Estados Selecionados, Índices de Crescimento de Óbitos
```{r states_plot, echo=FALSE, message=FALSE, warning=FALSE}
state_gl7s
```

## 5 - Capitais Selecionadas, Índices de Crescimento de Óbitos
```{r cities_plot, echo=FALSE, message=FALSE, warning=FALSE}
# city_gl7s
for( i in seq_along( city_gl7s ) )
  { city_gl7s[[ i ]] }
```


## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
